### 2020-12-09 05_Thesis/THESIS_LaTeX/pdf/CV/CV.tex
MNT checklist

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Osamu}{Katagiri}{ \urlstyle{same}\href{https://www.katagiri-mx.com/}{katagiri-mx.com} | \href{https://www.linkedin.com/in/osamu-k-84b2b940}{linkedin}\\ \href{mailto:osamu.katagiri@exatec.tec.mx}{osamu.katagiri@exatec.tec.mx}
}

@@

\subsection{Tecnológico de Monterrey}
\descript{MSc in Nanotechnology}
\location{Jan 2019 - Dec 2020 | Estado de México, MX}
\sectionsep

\subsection{Tecnológico de Monterrey}
\descript{BS in Digital Systems and Robotics}
\location{Aug2012 - May 2016 | Querétaro, MX}
\location{Cum. GPA: 3.6 / 4.0}
\sectionsep

@@

\section{Coursework}
\subsection{Graduate}
Thermodynamics of Materials \\
Nano-structured Materials \\
Plastics and Composites Engineering \\
{\footnotesize \textit{\textbf{Rheology \& Electrospinning}}} \\
\sectionsep

@@

\section{Experience}
\runsubsection{GE Aviation}
\descript{| Embedded Software Eng. }
\location{Jun 2018 - Dec 2019 | Querétaro, MX}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item At General Electric's Business \& General Aviation Power Software team, I develop and test critical software for Aviation Power products. I have high responsibility in the development and in the documentation of the features and interactions with other systems.
\end{tightemize}
\sectionsep

\runsubsection{GE Aviation}
\descript{| SW Edison Engineering Development Program }
\location{June 2016 – May 2018 | Querétaro, MX}
\begin{tightemize}
\item EEDP is an intensive program for people who have a passion for technology, a drive for technical excellence, and share in GE's core values. It is designed to accelerate participants' professional development through intense technical training.
\end{tightemize}
\sectionsep

@@

\section{Research}
\runsubsection{Macrophotoscience Reseach Group}
\descript{| MSc Student}
\location{Jan 2019 – Dec 2020 | Nuevo León, MX}
Worked with \textbf{\href{https://orcid.org/0000-0003-0455-5401}{Phd. Alan Aguirre}} and \textbf{\href{https://orcid.org/0000-0001-5325-0079}{Phd. Dora Medina}} to determine the electro-spunability of various polymer solutions for the fabrication of carbon nano-wires.
\sectionsep

@@

\section{Awards} 
\begin{tabular}{rll}
May 2018	& top 4\%                    & Software EEDP graduate at GE Aviation\\
Aug 2015	& 1\textsuperscript{st}/1000 & GE 9th Lean Challenge\\
Nov 2014	& 1\textsuperscript{st}/50   & GEIQ’s Robotics Project\\
\end{tabular}
\sectionsep

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Osamu}{Katagiri}{ \urlstyle{same}\href{https://www.katagiri-mx.com/}{katagiri-mx.com} | \href{https://www.linkedin.com/in/osamu-k-84b2b940}{linkedin}\\ \href{mailto:osamu.katagiri@exatec.tec.mx}{osamu.katagiri@exatec.tec.mx}\\
+52 55 2300 9176
}

@@

\subsection{Tecnológico de Monterrey}
\descript{MSc in Nanotechnology}
\location{Jan 2019 - Dec 2020 | Estado de México, MX}
\location{Cum. GPA: 3.8 / 4.0}
\sectionsep

\subsection{Tecnológico de Monterrey}
\descript{BS in Digital Systems and Robotics}
\location{Aug 2012 - May 2016 | Querétaro, MX}
\location{Cum. GPA: 3.5 / 4.0}
\sectionsep

@@

\section{Coursework}
\subsection{Graduate}
Nano-structured Materials \\
Carbon Nano-materials \\
Plastics and Composites Engineering \\
\textit{\textbf{Rheology \& Electrospinning}} \\
\sectionsep

@@

\section{Experience}
\runsubsection{GE Aviation}
\descript{| Embedded Software Eng. }
\location{Jun 2018 - Dec 2018 | Querétaro, MX}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item At General Electric's Business \& General Aviation (BGA) Power Software team, I develop and test critical software for Aviation Power products. I have high responsibility in the development and in the documentation of the features and interactions with other systems.
\end{tightemize}
\sectionsep

\runsubsection{GE Aviation}
\descript{| SW Edison Engineering Development Program }
\location{Jun 2016 – May 2018 | Querétaro, MX}
\begin{tightemize}
\item EEDP is an intensive program for people who have a passion for technology, a drive for technical excellence, and share in GE's core values. It is designed to accelerate participants' professional development through intense technical training.
\item 1st rotation at GEIQ-BGA software validation \& verification team
\item 2nd rotation at GEIQ-N\&G tools team
\item 3rd and 4th rotations at GEIQ-BGA software development team
\end{tightemize}
\sectionsep

@@

\section{Research}
\runsubsection{Macrophotoscience Reseach Group}
\descript{| MSc Student}
\location{Jan 2019 – Dec 2020 | Nuevo León, MX}
Worked with \textbf{\href{https://orcid.org/0000-0003-0455-5401}{Phd. Alan Aguirre}} and \textbf{\href{https://orcid.org/0000-0001-5325-0079}{Phd. Dora Medina}} to determine the electro-spinnability of various polymer solutions for the fabrication of carbon nano-wires.
\sectionsep

@@

\section{Awards} 
\begin{tabular}{rll}
May 2018	& top 4\%                   & Software EEDP graduate at GE Aviation\\
Aug 2015	& 1\textsuperscript{st}/100 & GE 9th Lean Challenge\\
Nov 2014	& 1\textsuperscript{st}/50  & GEIQ’s Robotics Project\\
\end{tabular}
\sectionsep
